Thermodynamic fragments in magic state theories

### 2021-02-12 magic_paper.tex
Added lemma that proves explicit expressions for n-copy wigner, it uses multinomial theorem, but no need for explicit reference outside the proof

@@

Consider a general $\epsilon$-noisy Strange state $\noisys$ in a thermal fragment $\O_{\gamma}$.
We can construct the Gibbs-rescaled distribution 
\begin{equation}
	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) = \widetilde{\rm{W}}_1(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
\end{equation}
which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is positive in regions $X,Y,Z$ and negative in region $1$.
    It attains a unique value in each region.
    The values and multiplicites can be read off as the term coefficients in~\cref{eq:g1}.
    }
    \label{fig:pd_split_thermal}
\end{figure}
In each region, we want to keep track of the number of phase space points it contains (i.e. the multiplicity) and the corresponding values of the Wigner distributions $\W{\noisys}, \W{\gamma}$ and the Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$. 
To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
\begin{align}\label{eq:g1}
	G_1(\noisys) &\coloneqq -\wn + 2\wp X + 3\wp Y + 3\wp Z \\
	\begin{split}
	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_0} + 2e^{-\beta E_0} X \\
	&\hspace{49pt} + 3e^{-\beta E_1} Y + 3e^{-\beta E_2} Z \big) 
	\end{split}
	\\
	\begin{split}
	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_0} + 2\wp e^{\beta E_0} X \\
	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 3\wp e^{\beta E_2} Z \big)
	\end{split}
\end{align}
The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.
Note that the negative Strange state Wigner component pairs with energy eigenvalue $E_0$ in region $1$.

An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$ which generates new regions of different slope.
In particular, it comprises exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and 
\begin{equation}
	\alpha \coloneqq i+j+k \leq n.
\end{equation}
For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$ or $\bmz \oplus \bmy$, where $\bmy \in Y$ and $\bmz \in Z$.
Note that there is no difference between e.g. regions $YZ$ and $ZY$, since multiplication of slopes is commutative. 
\nick{abuse of notation: I use X,Y,Z as sets and as variables that represent those sets}

The $n$-copy Wigner distributions $\W{\noisys\too{n}}, \W{\gamma\too{n}}$, and consequently the $n$-copy Gibbs-rescaled distribution $\widetilde{\rm{W}}_n = \widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}$ can be written as self-convolutions,
\begin{align}
	\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n) \nonumber\\
	&= \W{\noisys}(\bmx)\too{n} \\[10pt]
	\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n) \nonumber\\
	&= \W{\gamma}(\bmx)\too{n} \\[10pt]
	\widetilde{\rm{W}}_n(\bmx_1 \oplus \dots \oplus \bmx_n) &= \frac{\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)}{\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)} \\
	= \frac{\W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n)}{\W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n)} &= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} \nonumber\\
	&= \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}. \nonumber
\end{align}
Therefore, the values and multiplicites of the $n$-copy distributions are generated directly as a multinomial expansion of the $1$-copy expressions in~\cref{eq:g1}.
\begin{align}\label{eq:gn}
	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
\end{align}
where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
\begin{equation}
	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
\end{equation}

In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{equation}\label{eq:max_slope}
	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
\end{equation}
Notice that for $0 \leq \epsilon \leq \frac{3}{7}$, we have $\wn \geq \wp$.
Assume that $n$ is even (the analysis is similar for odd $n$). 
We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and its minimum value $0$ for
\begin{equation}
	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
We have
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

@@

Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. \nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C1)} \rightarrow \rm{(C2)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}

@@

>>>>

\subsubsection{Component-multiplicity pairs}

\nick{Probably will move this subsection to the earlier section where we discuss phase spaces in general}

In general, a $1$-copy $d$-dimensional state is defined exactly by its $d^2$ Wigner distribution $W$. 
The distribution $W$ can always be described by a set of $D \leq d^2$ component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
\begin{definition}
	Consider a $d^2$-dimensional distribution $W$ and a positive integer $D$. 
	We call the set of order pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
\end{definition}
Therefore, such a set that describes a distribution $W$ contains in its description each component of $W$ exactly once.
As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.

Consider two states $\rho_A, \rho_B$ with Wigner distributions $\W{\rho_A}, \W{\rho_B}$ described respectively by complete sets of component-multiplicity pairs 
\begin{equation}
	\{(w_i, m_i)\}_{i=1,\dots,D_A} \text{ and } \{(w_j', m_j')\}_{j=0,\dots,D_B}.
\end{equation}
The multiplicative property of the Wigner distribution over a composite phase space $\pd[d_A] \times \pd[d_B]$,
\begin{equation}
	\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B},
\end{equation}
implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$-dimensional and contains components of the form $w_i w_j'$. 
Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
This is true because all components are of the form $w_i w_j'$ and 
\begin{equation*}
	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2.
\end{equation*}

Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}\too{n}$.
\begin{lemma}\label{lem:ncopycomponents}
	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W\too{n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.

	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
	\begin{equation*}
	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
	\end{equation*}

	Then, $W\too{n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
\begin{align}
	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
\end{align}
\end{lemma}
\begin{proof}
	We proceed by induction.

	Assume $n = 1$.
	Let $\bmk_i \coloneqq (0,\dots,0,1,0,\dots,0)$ be a vector with its $i$-th component equal to 1 and 0's elsewhere.
	The set $C_D^1$ consists of all vectors of this form, i.e. 
\begin{equation*}
	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
\end{equation*}
	It is also true by direct calculation that
\begin{equation*}
	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
\end{equation*}
Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.

	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W\too{n}$.
	By construction, the distribution $W\too{(n+1)} = W\too{n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
\begin{equation}
	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
\end{equation}

	Consider the component sum of the distribution $W\too{(n+1)}$,
\begin{align*}
	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
\end{align*}
where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
\begin{align*}
	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
\end{align*}
We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.

We have achieved a regrouping of the distribution components.
Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
\begin{align*}
	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
\end{align*}
which is the dimension of $W\too{(n+1)}$.

Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W\too{n}$, completing the proof.
\end{proof}

\subsubsection{Distillation bounds}

@@

Consider a general $\epsilon$-noisy Strange state $\noisys$ in a thermal fragment $\O_{\gamma}$.
We can construct the Gibbs-rescaled distribution 
\begin{equation}
	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
\end{equation}
Notice that the Gibbs-rescaled distribution is multiplicative in general,
\begin{align}
	&\widetilde{\rm{W}}_{\rho_A \otimes \rho_B | \gamma_A \otimes \gamma_B}(\bmx_A \oplus \bmx_B) = \frac{\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B}}{\W[\bmx_A \oplus \bmx_B]{\gamma_A \otimes \gamma_B}} = \nonumber \\
	&\frac{\W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}}{\W[\bmx_A]{\gamma_A}\W[\bmx_B]{\gamma_B}} = \widetilde{\rm{W}}_{\rho_A | \gamma_A}(\bmx_A)\widetilde{\rm{W}}_{\rho_B  | \gamma_B}(\bmx_B).
\end{align}

We construct complete sets of component-multiplicity pairs and based on the distinct components of the Gibbs-rescaled distribution,
\begin{align}
	S(\noisys) &\coloneqq \{ (-\wn, 1), (\wp, 2), (\wp, 3), (\wp, 3) \} \\
	S(\gamma) &\coloneqq \Big\{ \left( \frac{e^{-\beta E_0}}{3\Z}, 1 \right), \left( \frac{e^{-\beta E_0}}{3\Z}, 2 \right), \nonumber\\
	&\hspace{23pt} \left( \frac{e^{-\beta E_1}}{3\Z}, 3 \right), \left( \frac{e^{-\beta E_2}}{3\Z}, 3 \right) \Big\} \\
	S(\noisys | \gamma) &\coloneqq \{ (-\wn 3\Z e^{\beta E_0}, 1), (\wp 3\Z e^{\beta E_0}, 2), \nonumber\\
	&\hspace{21pt} (\wp 3\Z e^{\beta E_1}, 3), (\wp 3\Z e^{\beta E_2}, 3) \}
\end{align}

There are four distinct component-multiplicity pairs for the Gibbs-rescaled distribution, so in order to use~\cref{lem:ncopycomponents} to find the components of the $n$-copy distributions, we first define an index vector
\begin{equation}
	\bmq \coloneqq (n-\alpha,i,j,k),
\end{equation}
where $i,j,k$ are non-negative integers that satisfy 
\begin{equation*}
	i+j+k \eqqcolon \alpha \leq n.
\end{equation*}
The $n$-copy

\begin{align}\label{eq:gn}
	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
\end{align}
where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
\begin{equation}
	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
\end{equation}

In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{equation}\label{eq:max_slope}
	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}},
\end{equation}
where $0 \leq i,j,k \leq n$ and $i+j+k \eqqcolon \alpha \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $\wn \geq \wp$.
Assume that $n$ is even. 
We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ (greater than $1$).
The threshold value of $1$ is achieved when the noise level $\epsilon$ is equal to
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise level threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
\begin{equation}
	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
For $\beta > \beta_{\rm{th}}$, $\epsilon_{\rm{th}}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = \beta_{\rm{th}}^{-1} \ln2.
\end{equation}

The maximum slope finally is
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

@@

Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. \nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}

@@

which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is positive in regions $X,Y,Z$ and negative in region $1$.
    It attains a unique value in each region.
    The values and multiplicites can be read off as the term coefficients in~\cref{eq:g1}.
    }
    \label{fig:pd_split_thermal}
\end{figure}
In each region, we want to keep track of the number of phase space points it contains (i.e. the multiplicity) and the corresponding values of the Wigner distributions $\W{\noisys}, \W{\gamma}$ and the Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$. 
To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
\begin{align}\label{eq:g1}
	G_1(\noisys) &\coloneqq -\wn + 2\wp X + 3\wp Y + 3\wp Z \\
	\begin{split}
	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_0} + 2e^{-\beta E_0} X \\
	&\hspace{49pt} + 3e^{-\beta E_1} Y + 3e^{-\beta E_2} Z \big) 
	\end{split}
	\\
	\begin{split}
	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_0} + 2\wp e^{\beta E_0} X \\
	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 3\wp e^{\beta E_2} Z \big)
	\end{split}
\end{align}
The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.
Note that the negative Strange state Wigner component pairs with energy eigenvalue $E_0$ in region $1$.
